---
title: '`r rstudioapi::getSourceEditorContext()$path %>% basename() %>% gsub(pattern = "\\.Rmd",replacement = "")`' 
author: "Avishai Wizel"
date: '`r Sys.time()`'
output: 
  html_notebook: 
    code_folding: hide
    toc: yes
    toc_collapse: yes
    toc_float: 
      collapsed: FALSE
    number_sections: true
    toc_depth: 1
---



# Functions

```{r warning=FALSE}
```

# Data

```{r}
acc_immune = LoadH5Seurat(file = "./Data/acc_immune.h5seurat")
```

```{r}
library("readxl")
signatures <- read_excel("./Data/Shengjin_et al_DataSheet_1.xlsx", sheet = "Gene Signature",skip = 42,col_names = F)
signatures = signatures %>% t() %>% as.data.frame() %>% janitor::row_to_names(1) %>% dplyr::filter(!row_number() %in% c(1))
```



# log TMP signatures {.tabset}
```{r results='asis'}
acc_immune = FindVariableFeatures(object = acc_immune,nfeatures = 5000,verbose = F)
for (col in 1:ncol(signatures)) {
  genes = signatures[,col] %>% na.omit() %>% as.vector() %>% intersect(VariableFeatures(acc_immune))
  if (length(genes) == 0 ){
    print("skip")
    next
  }
  score = acc_immune@assays$RNA@data[genes,] %>% colMeans()
  acc_immune = AddMetaData(object = acc_immune,metadata = score, col.name = names(signatures)[col])
  print_tab(FeaturePlot(object = acc_immune,features = names(signatures)[col]),title = names(signatures)[col])

}

```
# scaled data signatures {.tabset}

```{r results='asis'}
acc_immune = FindVariableFeatures(object = acc_immune,nfeatures = 5000,verbose = F)
for (col in 1:ncol(signatures)) {
  genes = signatures[,col] %>% na.omit() %>% as.vector() %>% intersect(VariableFeatures(acc_immune))
  if (length(genes) == 0 ){
    print("skip")
    next
  }
  score = acc_immune@assays$RNA@scale.data[genes,] %>% colMeans()
  acc_immune = AddMetaData(object = acc_immune,metadata = score, col.name = names(signatures)[col])
  print_tab(FeaturePlot(object = acc_immune,features = names(signatures)[col]),title = names(signatures)[col])

}


# acc_immune <- AddModuleScore(
#   object = acc_immune,
#   features = list(genes),
#   ctrl = 5,
#   name = names(signatures)[col]
# )
# FeaturePlot(object = acc_immune,features = "Central_memory_CD4_T_cel1")


```
# Clusters
```{r}
acc_immune <- FindClusters(acc_immune, resolution = 1,verbose = F)
DimPlot(acc_immune,label = T)
```

```{r}
lapply(c("dplyr","Seurat","HGNChelper"), library, character.only = T)
source("https://raw.githubusercontent.com/IanevskiAleksandr/sc-type/master/R/gene_sets_prepare.R"); source("https://raw.githubusercontent.com/IanevskiAleksandr/sc-type/master/R/sctype_score_.R")

db_ = "https://raw.githubusercontent.com/IanevskiAleksandr/sc-type/master/ScTypeDB_full.xlsx";
tissue = "Immune system" # e.g. Immune system,Pancreas,Liver,Eye,Kidney,Brain,Lung,Adrenal,Heart,Intestine,Muscle,Placenta,Spleen,Stomach,Thymus 

# prepare gene sets
gs_list = gene_sets_prepare(db_, tissue)
```

# ScType

```{r}
es.max = sctype_score(scRNAseqData = acc_immune[["RNA"]]@scale.data, scaled = TRUE, 
                      gs = gs_list$gs_positive, gs2 = gs_list$gs_negative) 
# merge by cluster
cL_resutls = do.call("rbind", lapply(unique(acc_immune@meta.data$seurat_clusters), function(cl){
    es.max.cl = sort(rowSums(es.max[ ,rownames(acc_immune@meta.data[acc_immune@meta.data$seurat_clusters==cl, ])]), decreasing = !0)
    head(data.frame(cluster = cl, type = names(es.max.cl), scores = es.max.cl, ncells = sum(acc_immune@meta.data$seurat_clusters==cl)), 10)
}))
sctype_scores = cL_resutls %>% group_by(cluster) %>% top_n(n = 1, wt = scores)  

# set low-confident (low ScType score) clusters to "unknown"
sctype_scores$type[as.numeric(as.character(sctype_scores$scores)) < sctype_scores$ncells/4] = "Unknown"
print(sctype_scores[,1:3])

acc_immune@meta.data$cell_identity = ""
for(j in unique(sctype_scores$cluster)){
  cl_type = sctype_scores[sctype_scores$cluster==j,]; 
  acc_immune@meta.data$cell_identity[acc_immune@meta.data$seurat_clusters == j] = as.character(cl_type$type[1])
}

DimPlot(acc_immune, reduction = "umap", label = F, repel = TRUE, group.by = 'cell_identity')  
```

```{r}
es.max = sctype_score(scRNAseqData = acc_immune[["RNA"]]@scale.data, scaled = TRUE, 
                      gs = gs_list$gs_positive, gs2 = gs_list$gs_negative) 
# merge by cluster
cL_resutls = do.call("rbind", lapply(unique(acc_immune@meta.data$seurat_clusters), function(cl){
    es.max.cl = sort(rowSums(es.max[ ,rownames(acc_immune@meta.data[acc_immune@meta.data$seurat_clusters==cl, ])]), decreasing = !0)
    head(data.frame(cluster = cl, type = names(es.max.cl), scores = es.max.cl, ncells = sum(acc_immune@meta.data$seurat_clusters==cl)), 10)
}))
sctype_scores = cL_resutls %>% group_by(cluster) %>% top_n(n = 1, wt = scores)  

# set low-confident (low ScType score) clusters to "unknown"
sctype_scores$type[as.numeric(as.character(sctype_scores$scores)) < sctype_scores$ncells/4] = "Unknown"
print(sctype_scores[,1:3])

acc_immune@meta.data$cell_identity = ""
for(j in unique(sctype_scores$cluster)){
  cl_type = sctype_scores[sctype_scores$cluster==j,]; 
  acc_immune@meta.data$cell_identity[acc_immune@meta.data$seurat_clusters == j] = as.character(cl_type$type[1])
}

DimPlot(acc_immune, reduction = "umap", label = TRUE, repel = TRUE, group.by = 'cell_identity')  
```



```{r}
cL_resutls
```


```{r}
acc_immune = SetIdent(object = acc_immune,value = "cell_identity")
g1_treat <- WhichCells(acc_immune, idents = c( "Macrophages"))
DimPlot(acc_immune, label=F, cells.highlight= g1_treat, cols.highlight = c( "red"), cols= "grey")
```

```{r}
FindMarkers(object = acc_immune,ident.1 = "1",densify = T)
```

```{r}
FeaturePlot(object = acc_immune,features = "GATA3")
```


```{r fig.width=12}
scores_data = AverageExpression(object = acc_immune,features = names(signatures))
pheatmap(scores_data)
```

```{r fig.height=8, fig.width=10}
FeaturePlot(object = acc_immune,features = names(signatures)[1:6])
FeaturePlot(object = acc_immune,features = names(signatures)[7:13])
FeaturePlot(object = acc_immune,features = names(signatures)[14:17])
FeaturePlot(object = acc_immune,features = names(signatures)[20:26])
FeaturePlot(object = acc_immune,features = names(signatures)[27:28])

```


# Immune markers
```{r fig.height=8, fig.width=10}
FeaturePlot(acc_immune, features = c("CD4","MS4A1", "SELL", "CD3E",  "S100A4","CD14","GNLY","MS4A1"))
```
# assign cell type
```{r fig.height=6, fig.width=8}
acc_immune <- RenameIdents(object = acc_immune, 
                               "0" = "Naive CD4+ T",
                               "1" = "Memory CD4+",
                               "2" = "CD14+ Mono",
                               "3" = "Memory CD4+",
                               "4" = "CD8+ T",
                               "5" = "B",
                               "6" = "Naive CD4+ T",
                               "7" = "Memory CD4+",
                               "8" = "Memory CD4+")
acc_immune$cell_identity = acc_immune@active.ident
DimPlot(object = acc_immune,label = T)
```

# Antigen presenting machinery {.tabset}
```{r}
apm_genes = c("HLA-A","HLA-B","HLA-C","B2M","TAP1","TAP2", "TAPBP")
apm_score = FetchData(acc_immune,vars = apm_genes,slot = "data") %>% rowMeans()
acc_immune = AddMetaData(object = acc_immune,metadata = apm_score,col.name = "APM_score")
```

```{r fig.height=8, fig.width=10, results='asis'}
print_tab(plt = FeaturePlot(acc_immune,features = apm_genes),title = "genes")
print_tab(plt = FeaturePlot(acc_immune,features = "APM_score"),title = "score")
```

# Exhaustion markers
```{r fig.height=8, fig.width=10}
exhausted_genes = c("PDCD1","CD244","CD160","CTLA4","HAVCR2")
FeaturePlot(acc_immune,features = exhausted_genes)
```
# Immune receptors
```{r fig.height=8, fig.width=10}
receptors = c("CCR3", "CCR4", "CCR10","CXCR2", "CXCR3", "CXCR4", "IL17A")
FeaturePlot(acc_immune,features = receptors)

```
# CellphoneDB
```{r}
acc_cancer_cells = readRDS("/sci/labs/yotamd/lab_share/avishai.wizel/R_projects/ACC_microenv/Data/acc_cancer_no146_primaryonly15k_cancercells.rds")
```



```{r}
# merge cancer and immune
common_genes = intersect(rownames(acc_cancer_cells),rownames(acc_immune))
acc_cancer_and_cd45 = merge(acc_cancer_cells[common_genes,],acc_immune[common_genes,])
```

```{r}
  #write metadata

#create lum or myo
lum_over_myo = FetchData(object = acc_cancer_cells,vars = "luminal_over_myo")
lum_over_myo$lum_or_myo = "Unknown"
lum_over_myo$lum_or_myo [lum_over_myo$luminal_over_myo>1]  = "Luminal"
lum_over_myo$lum_or_myo [lum_over_myo$luminal_over_myo<(-1)]  = "Myo"
lum_or_myo = lum_over_myo[,"lum_or_myo",drop = F]
names(lum_or_myo)[1] = "cell_identity"

# combine
immune_identity =FetchData(object = acc_immune,vars = "cell_identity")
all_identity= rbind(lum_or_myo,immune_identity )

#rename and sort columns
all_identity$barcode_sample = rownames(all_identity)
all_identity = all_identity %>% rename(cell_type = cell_identity)
all_identity = all_identity[,c(2,1)]


write.table(x = all_identity,file = "./Data/CellphoneDB/metadata.tsv",row.names =F,sep = "\t")
```

```{r}
#write normalized counts
count_matrix = as.data.frame(acc_cancer_and_cd45@assays[["RNA"]]@data)
fwrite(count_matrix, file = "./Data/CellphoneDB/counts.txt",sep = "\t",row.names = T)
```


```{python include=FALSE}
#download database
import pandas as pd
import glob
import os
# -- Version of the databse
cpdb_version = 'v4.1.0'

# -- Path where the input files to generate the database are located
cpdb_target_dir = os.path.join('./Data/CellphoneDB/', cpdb_version)

# Download database
from cellphonedb.utils import db_utils
db_utils.download_database(cpdb_target_dir, cpdb_version)
```

```{python include=FALSE}
from cellphonedb.src.core.methods import cpdb_statistical_analysis_method

deconvoluted, means, pvalues, significant_means = cpdb_statistical_analysis_method.call(
    cpdb_file_path = "./Data/CellphoneDB/v4.1.0/cellphonedb.zip",                 # mandatory: CellPhoneDB database zip file.
    meta_file_path = "./Data/CellphoneDB/metadata.tsv",                 # mandatory: tsv file defining barcodes to cell label.
    counts_file_path = "./Data/CellphoneDB/counts.txt",             # mandatory: normalized count matrix.
    counts_data = 'hgnc_symbol',                     # defines the gene annotation in counts matrix.
    output_path = "./Data/CellphoneDB/output",                          # Path to save results.
)
```


```{r}
library(ktplots)
acc_cancer_and_cd45$cell_type = all_identity[,2,drop = F] # add cells identities to seurat

#read data:
pvals =  read.delim(file = "./Data/CellphoneDB/output/statistical_analysis_pvalues_07_19_2023_12:16:16.txt", check.names = FALSE)
means = read.delim(file = "./Data/CellphoneDB/output/statistical_analysis_means_07_19_2023_12:16:16.txt", check.names = FALSE)

```

# significant interactions heatmap
```{r}
plot_cpdb_heatmap(scdata = acc_cancer_and_cd45, idents = 'cell_type',pvals =  pvals,main = "Number of significant interactions",alpha = 0.05)
```

# Costimulatory interactions {.tabset}
```{r fig.height=8, results='asis'}

print_tab(plt = 
            plot_cpdb(cell_type1 = 'CD', cell_type2 = 'Luminal', scdata = acc_cancer_and_cd45,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = 'costimulatory',return_table = F,max_size = 3,p.adjust.method = "fdr",keep_significant_only = T,cluster_rows = F)+
            ggtitle("costimulatory Luminal")
  ,title = "Luminal")

print_tab(plt = 
            plot_cpdb(cell_type1 = 'CD', cell_type2 = 'Myo', scdata = acc_cancer_and_cd45,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = 'costimulatory',return_table = F,max_size = 3,p.adjust.method = "fdr",keep_significant_only = T,cluster_rows = F)+
            ggtitle("costimulatory Myo")
  ,title = "Myo")
```

# Coinhibitory interactions {.tabset}

```{r fig.height=5,results='asis'}

print_tab(plot_cpdb(cell_type1 = 'CD', cell_type2 = 'Luminal', scdata = acc_cancer_and_cd45,
          idents = 'cell_type', means = means, pvals = pvals,
          gene.family = 'coinhibitory',return_table = F,max_size = 4,p.adjust.method = "fdr",keep_significant_only = F,cluster_rows = F)+
  ggtitle("coinhibitory Luminal"),title = "Luminal")

print_tab(plot_cpdb(cell_type1 = 'CD', cell_type2 = 'Myo', scdata = acc_cancer_and_cd45,
          idents = 'cell_type', means = means, pvals = pvals,
          gene.family = 'coinhibitory',return_table = F,max_size = 4,p.adjust.method = "fdr",keep_significant_only = F,cluster_rows = F)+
  ggtitle("coinhibitory Myo"),title = "Myo")
```

# Chemokines interactions {.tabset}
```{r fig.height=6, results='asis'}
print_tab(
  plot_cpdb(cell_type1 = 'CD', cell_type2 = 'Luminal', scdata = acc_cancer_and_cd45,
          idents = 'cell_type', means = means, pvals = pvals,
          gene.family = 'chemokines',return_table = F,max_size = 4,p.adjust.method = "fdr",keep_significant_only = F,cluster_rows = F)+
  ggtitle("chemokines Luminal"),title = "Luminal")

print_tab(
  plot_cpdb(cell_type1 = 'CD', cell_type2 = 'Myo', scdata = acc_cancer_and_cd45,
          idents = 'cell_type', means = means, pvals = pvals,
          gene.family = 'chemokines',return_table = F,max_size = 4,p.adjust.method = "fdr",keep_significant_only = F,cluster_rows = F)+
  ggtitle("chemokines Myo"),title = "Myo")
```
# Chemokine ligands {.tabset}
```{r results='asis'}
print_tab(plot_cpdb(cell_type1 = 'CD', cell_type2 = 'Myo', scdata = acc_cancer_and_cd45,
    idents = 'cell_type', means = means, pvals = pvals,
 genes = c("CXCL1\\D", "CXCL2\\D","CXCL3\\D","CXCL17","C3","CXCL14"),return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F) 
 ,title = "Myo")

print_tab(plot_cpdb(cell_type1 = 'CD', cell_type2 = 'Luminal', scdata = acc_cancer_and_cd45,
    idents = 'cell_type', means = means, pvals = pvals,
  genes = c("CXCL1\\D", "CXCL2\\D","CXCL3\\D","CXCL17","C3","CXCL14"),return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F) 
,title = "Luminal")

```
# CCL22 and CCL28 {.tabset}
```{r results='asis'}
print_tab(plot_cpdb(cell_type1 = 'CD', cell_type2 = 'Myo', scdata = acc_cancer_and_cd45,
    idents = 'cell_type', means = means, pvals = pvals,
 genes = c("CCL22", "CCL28" ),return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F),title = "Myo")

print_tab(plot_cpdb(cell_type1 = 'CD', cell_type2 = 'Luminal', scdata = acc_cancer_and_cd45,
    idents = 'cell_type', means = means, pvals = pvals,
  genes = c("CCL22", "CCL28" ),return_table = F,max_size = 6,p.adjust.method = "fdr" ,keep_significant_only = F),title = "Luminal")



```

```{r fig.height=6}
plot_cpdb(cell_type1 = 'CD', cell_type2 = 'Myo', scdata = acc_cancer_and_cd45,
    idents = 'cell_type', means = means, pvals = pvals,
 genes = c("JAG", "MYB" ),return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F) 

plot_cpdb(cell_type1 = 'CD', cell_type2 = 'Luminal', scdata = acc_cancer_and_cd45,
    idents = 'cell_type', means = means, pvals = pvals,
  genes = c("JAG", "MYB" , "NOTCH","HES1","HEY"),return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F) 


```
<script src="https://hypothes.is/embed.js" async></script>

