---
title: '`r rstudioapi::getSourceEditorContext()$path %>% basename() %>% gsub(pattern = "\\.Rmd",replacement = "")`' 
author: "Avishai Wizel"
date: '`r Sys.time()`'
output: 
  html_notebook: 
    code_folding: hide
    toc: yes
    toc_collapse: yes
    toc_float: 
      collapsed: FALSE
    number_sections: true
    toc_depth: 1
---



# Functions

```{r warning=FALSE}

scAssign_db <- function(tissue) {
  lapply(c("dplyr","Seurat","HGNChelper"), library, character.only = T)
  source("https://raw.githubusercontent.com/IanevskiAleksandr/sc-type/master/R/gene_sets_prepare.R"); source("https://raw.githubusercontent.com/IanevskiAleksandr/sc-type/master/R/sctype_score_.R")
  
  db_ = "https://raw.githubusercontent.com/IanevskiAleksandr/sc-type/master/ScTypeDB_full.xlsx";
  tissue = tissue # e.g. Immune system,Pancreas,Liver,Eye,Kidney,Brain,Lung,Adrenal,Heart,Intestine,Muscle,Placenta,Spleen,Stomach,Thymus 
  
  # prepare gene sets
  gs_list = gene_sets_prepare(db_, tissue)
  return(gs_list)
}

scAssign <- function(seuratObj,gs_list) {
  es.max = sctype_score(scRNAseqData = seuratObj[["RNA"]]@scale.data, scaled = TRUE, 
                      gs = gs_list$gs_positive, gs2 = gs_list$gs_negative) 
  # merge by cluster
  cL_resutls = do.call("rbind", lapply(unique(seuratObj@meta.data$seurat_clusters), function(cl){
      es.max.cl = sort(rowSums(es.max[ ,rownames(seuratObj@meta.data[seuratObj@meta.data$seurat_clusters==cl, ])]), decreasing = !0)
      head(data.frame(cluster = cl, type = names(es.max.cl), scores = es.max.cl, ncells = sum(seuratObj@meta.data$seurat_clusters==cl)), 10)
  }))
  sctype_scores = cL_resutls %>% group_by(cluster) %>% top_n(n = 1, wt = scores)  
  
  # set low-confident (low ScType score) clusters to "unknown"
  sctype_scores$type[as.numeric(as.character(sctype_scores$scores)) < sctype_scores$ncells/4] = "Unknown"
  print(sctype_scores[,1:3])
  
  seuratObj@meta.data$cell_identity = ""
  for(j in unique(sctype_scores$cluster)){
    cl_type = sctype_scores[sctype_scores$cluster==j,]; 
    seuratObj@meta.data$cell_identity[seuratObj@meta.data$seurat_clusters == j] = as.character(cl_type$type[1])
  }
  return(seuratObj)
}

```

# Data

```{r}
acc_immune = LoadH5Seurat(file = "./Data/acc_immune_5KvarGenes.h5seurat")
```

# Clustering
```{r}
acc_immune <- FindClusters(acc_immune, resolution = 5,verbose = F, algorithm = 1)
DimPlot(acc_immune,label = T)
```



# Cell type assignment  {.tabset}

## cluster scores
```{r echo=TRUE, results='asis'}
gs_list = scAssign_db(tissue = "Immune system")
acc_immune %<>% scAssign(gs_list = gs_list)
```



```{r echo=TRUE, results='asis'}
acc_immune %<>%  SetIdent(value = "cell_identity")
print_tab(DimPlot(acc_immune,group.by = "cell_identity"),title = "UMAP")
print_tab(plt = acc_immune$cell_identity %>% table() %>% as.data.frame(), title = "cell count")
```
# Markers
```{r fig.height=8, fig.width=10}
FeaturePlot(acc_immune, features = c("CD8A","MS4A1", "CD4","CD14","MS4A2"))
```



# Markers heatmaps {.tabset}
```{r fig.height=8, fig.width=12, echo=TRUE, results='asis'}
print_tab(plt = 
            DoHeatmap(acc_immune, features =c("CD8A","MS4A1", "CD4","CD14","MS4A2"), size = 3,slot = "data")
          ,title = "markers")

print_tab(plt = 
            DoHeatmap(subset(acc_immune,subset = cell_identity == "Macrophages"), features
                      =gs_list$gs_positive$Macrophages, size = 3,slot = "data")
          ,title = "Macrophages markers")

```

# Cell type correlation
```{r}
acc_immune = SetIdent(object = acc_immune,value = "cell_identity")
correlation = cor(AverageExpression(object = acc_immune) %>% as.data.frame())
colnames(correlation) <- gsub(pattern = "RNA.",replacement = "",x = colnames(correlation))
rownames(correlation) <- gsub(pattern = "RNA.",replacement = "",x = rownames(correlation))

pheatmap(mat = correlation,main = "Expression correlation")
```

# Antigen presenting machinery {.tabset}
```{r}
apm_genes = c("HLA-A","HLA-B","HLA-C","B2M","TAP1","TAP2", "TAPBP")
apm_score = FetchData(acc_immune,vars = apm_genes,slot = "data") %>% rowMeans()
acc_immune = AddMetaData(object = acc_immune,metadata = apm_score,col.name = "APM_score")
```

```{r fig.height=8, fig.width=10, results='asis'}
print_tab(plt = FeaturePlot(acc_immune,features = apm_genes),title = "genes")
print_tab(plt = FeaturePlot(acc_immune,features = "APM_score"),title = "score")
```

# Exhaustion markers
```{r fig.height=8, fig.width=10}
exhausted_genes = c("PDCD1","CD244","CD160","CTLA4","HAVCR2")
FeaturePlot(acc_immune,features = exhausted_genes)
```
# Immune receptors
```{r fig.height=8, fig.width=10}
receptors = c("CCR3", "CCR4", "CCR10","CXCR2", "CXCR3", "CXCR4", "IL17A")
FeaturePlot(acc_immune,features = receptors)
```

# CellphoneDB
```{r}
acc_cancer_cells_pri = readRDS("/sci/labs/yotamd/lab_share/avishai.wizel/R_projects/ACC_microenv/Data/acc_cancer_no146_primaryonly15k_cancercells.rds")
acc_caf = readRDS("/sci/labs/yotamd/lab_share/ACC/ACC_sc/analysis/acc_tpm_nCount_mito_no146_cafs.rds")
acc_immune_pri = subset(acc_immune, subset = origin == "Primary")
```


```{r}
# merge cancer and immune
common_genes = intersect(rownames(acc_cancer_cells_pri),rownames(acc_immune_pri)) %>% intersect(rownames(acc_caf_cells))
acc_cancer_and_cd45 = merge(acc_cancer_cells_pri[common_genes,],acc_immune_pri[common_genes,])
overlapping_cells = colnames(acc_cancer_cells_pri) %>% intersect(colnames(acc_caf)) 
acc_cancer_cd45_caf = merge(acc_cancer_and_cd45[common_genes,],acc_caf_cells[common_genes,!colnames(acc_caf_cells) %in% overlapping_cells] )

```

```{r}
  #write metadata

#create lum or myo
lum_over_myo = FetchData(object = acc_cancer_cells_pri,vars = "luminal_over_myo")
lum_over_myo$lum_or_myo = "Unknown"
lum_over_myo$lum_or_myo [lum_over_myo$luminal_over_myo>1]  = "Luminal"
lum_over_myo$lum_or_myo [lum_over_myo$luminal_over_myo<(-1)]  = "Myo"
lum_or_myo = lum_over_myo[,"lum_or_myo",drop = F]
names(lum_or_myo)[1] = "cell_identity"
lum_or_myo = lum_or_myo %>% filter(cell_identity != "Unknown") #remove unknown cells
  
# combine
immune_identity =FetchData(object = acc_immune_pri,vars = "cell_identity")
caf_identity =FetchData(object = acc_caf_cells,vars = "cell.type")
names(caf_identity)[1] = "cell_identity"
all_identity = do.call("rbind", list(lum_or_myo, immune_identity, caf_identity))

#rename and sort columns
all_identity$barcode_sample = rownames(all_identity)
all_identity = all_identity %>% rename(cell_type = cell_identity)
all_identity = all_identity[,c(2,1)]


```

```{r}
write.table(x = all_identity,file = "./Data/CellphoneDB/metadata_primary.tsv",row.names =F,sep = "\t")
```

```{r}
#write normalized counts
acc_cancer_cd45_caf = acc_cancer_cd45_caf[,rownames(all_identity)]
count_matrix = as.data.frame(acc_cancer_cd45_caf@assays[["RNA"]]@data)
fwrite(count_matrix, file = "./Data/CellphoneDB/counts_primary.txt",sep = "\t",row.names = T)
```




```{python include=FALSE}
#download database
import pandas as pd
import glob
import os
# -- Version of the databse
cpdb_version = 'v4.1.0'

# -- Path where the input files to generate the database are located
cpdb_target_dir = os.path.join('./Data/CellphoneDB/', cpdb_version)

# Download database
from cellphonedb.utils import db_utils
db_utils.download_database(cpdb_target_dir, cpdb_version)
```

```{python include=FALSE}
from cellphonedb.src.core.methods import cpdb_statistical_analysis_method

deconvoluted, means, pvalues, significant_means = cpdb_statistical_analysis_method.call(
    cpdb_file_path = "./Data/CellphoneDB/v4.1.0/cellphonedb.zip",                 # mandatory: CellPhoneDB database zip file.
    meta_file_path = "./Data/CellphoneDB/metadata_primary.tsv",                 # mandatory: tsv file defining barcodes to cell label.
    counts_file_path = "./Data/CellphoneDB/counts_primary.txt",             # mandatory: normalized count matrix.
    counts_data = 'hgnc_symbol',                     # defines the gene annotation in counts matrix.
    output_path = "./Data/CellphoneDB/output_primary",                          # Path to save results.
)
```   


```{r}
library(ktplots)
library(reticulate)
acc_cancer_cd45_caf$cell_type = all_identity[,2,drop = F] # add cells identities to Seurat

#read data:
pvals =  py$pvalues
means = py$means

#or:
pvals = read.delim("./Data/CellphoneDB/output_primary/statistical_analysis_pvalues_08_01_2023_16:13:32.txt",check.names = F)
means = read.delim("./Data/CellphoneDB/output_primary/statistical_analysis_means_08_01_2023_16:13:32.txt",check.names = F)

```

# significant interactions heatmap
```{r}
plot_cpdb_heatmap(scdata = acc_cancer_cd45_caf, idents = 'cell_type',pvals =  pvals,main = "Number of significant interactions",alpha = 0.05,treeheight_row = 50)
```



```{r}

trace(plot_cpdb,edit = T)
untrace(plot_cpdb)
plot_cpdb_with_col_clustering = plot_cpdb
to_insert =quote(
   if (ncol(means_mat) > 2) {
              d <- dist(as.data.frame(t(means_mat)))
              h <- hclust(d)
              means_mat <- means_mat[, h$order, drop = FALSE]
              pvals_mat <- pvals_mat[, h$order, drop = FALSE]
              plot(h, main = cell_type2)
  }
)


body(plot_cpdb_with_col_clustering) <- body(plot_cpdb_with_col_clustering) %>% as.list %>% append(to_insert,after =  41) %>% as.call
trace(plot_cpdb_with_col_clustering,edit = T)
```



```{r}
uniq_interactions <- function(cell_type1, cell_type2_a ,cell_type2_b, gene.family = NULL,genes = NULL) {
  require(purrr)
  a = plot_cpdb(cell_type1 = cell_type1, cell_type2 =cell_type2_a, scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = gene.family,return_table = T, p.adjust.method = "fdr",keep_significant_only = T, genes = genes)
  
  b = plot_cpdb(cell_type1 = cell_type1, cell_type2 = cell_type2_b, scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = gene.family,return_table = T,p.adjust.method = "fdr",keep_significant_only = T, genes = genes)
  
  
  all = list()
  i=0
  nelements = a$Var2 %>% unique() %>% length()
  a_couples = a$Var2 %>% unique()%>% as.vector()  
  b_couples = b$Var2 %>% unique()%>% as.vector()  
  for (i in 1:nelements) {
    sig_couples_a = a %>% filter(Var2 == a_couples[i]) %>% filter(pvals_adj <= 0.05) %>%  pull(Var1) %>% as.vector()  
    sig_couples_b = b %>% filter(Var2 == b_couples[i]) %>% filter(pvals_adj <= 0.05) %>%  pull(Var1) %>% as.vector()  
    only_in_a = sig_couples_a[! sig_couples_a %in% sig_couples_b]
    all[[a_couples[i]]] = only_in_a 
    i = i+1
  }
  all = t(map_dfr(all, ~as_tibble(t(.)))) %>% as.data.frame() %>%  set_names(a_couples)
  return(all)
}

```   

# All interactions {.tabset}
```{r fig.height=12, fig.width=20, results='asis'}
plot_cpdb_with_col_clustering(cell_type1 = 'CD|B|Natural|mono|Macro', cell_type2 = 'Luminal', scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = NULL,return_table = F,max_size = 3,p.adjust.method = "fdr",keep_significant_only = T,cluster_rows = T)+
            ggtitle("all Luminal")+
theme(axis.text.y=element_blank(),
      axis.ticks.y=element_blank())+
  plot_cpdb_with_col_clustering(cell_type1 = 'CD|B|Natural|mono|Macro', cell_type2 = 'Myo', scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = NULL,return_table = F,max_size = 3,p.adjust.method = "fdr",keep_significant_only = T,cluster_rows = T)+
            ggtitle("all Myo")+
theme(axis.text.y=element_blank(),
      axis.ticks.y=element_blank())
      
      
print_tab(plt = 
            plot_cpdb(cell_type1 = 'CD|B|FC', cell_type2 = 'Luminal', scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = NULL,return_table = F,max_size = 3,p.adjust.method = "fdr",keep_significant_only = T,cluster_rows = T)+
            ggtitle("all Luminal")+
theme(axis.text.y=element_blank(),
      axis.ticks.y=element_blank())
  ,title = "Luminal")

print_tab(plt = 
            plot_cpdb(cell_type1 = 'CD|B|FC', cell_type2 = 'Myo', scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = NULL,return_table = F,max_size = 3,p.adjust.method = "fdr",keep_significant_only = T,cluster_rows = T)+
            ggtitle("all Myo")+
theme(axis.text.y=element_blank(),
      axis.ticks.y=element_blank())
  ,title = "Luminal")


print_tab(plt = 
            plot_cpdb(cell_type1 = 'CD|B|FC', cell_type2 = 'Myo', scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = 'costimulatory',return_table = F,max_size = 3,p.adjust.method = "fdr",keep_significant_only = T,cluster_rows = F)+
            ggtitle("Costimulatory Myo")
  ,title = "Myo")

print_tab(plt = 
            plot_cpdb(cell_type1 = 'CD|B|FC', cell_type2 = 'CAF', scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = 'costimulatory',return_table = F,max_size = 3,p.adjust.method = "fdr",keep_significant_only = T,cluster_rows = F)+
            ggtitle("Costimulatory CAF")
  ,title = "CAF")

print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|FC',cell_type2_a  = 'Luminal',cell_type2_b = "Myo",gene.family = "Costimulatory")
,title = "unique in luminal")


print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|FC',cell_type2_a  = 'Myo',cell_type2_b = "Luminal",gene.family = "Costimulatory")
,title = "unique in myo")

print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|FC',cell_type2_a  = 'CAF',cell_type2_b = "Myo|Luminal",gene.family = "Costimulatory")
,title = "unique in CAF")
```

```{r}
acc_immune$specific_identity = acc_immune$cell_identity
acc_immune %<>% SetIdent(value = "specific_identity")
acc_immune <- RenameIdents(acc_immune, 'Naive CD4+ T cells' = 'CD4+', 'Effector CD8+ T cells' = 'CD8+','CD8+ NKT-like cells' = "CD8+", 'Naive CD8+ T cells' = "CD8+", 'Effector CD4+ T cells' = "CD4+")
acc_immune[["cell_identity"]] <- Idents(object = acc_immune)
```

```{r}
SeuratDisk::SaveH5Seurat(object = acc_immune,filename = "./Data/acc_immune_5KvarGenes_V2_cellIdentity.h5seurat")
```

# Coinhibitory interactions {.tabset}

```{r fig.height=5,results='asis'}

print_tab(plot_cpdb(cell_type1 = 'CD|B|FC', cell_type2 = 'Luminal', scdata = acc_cancer_cd45_caf,
          idents = 'cell_type', means = means, pvals = pvals,
          gene.family = 'coinhibitory',return_table = F,max_size = 4,p.adjust.method = "fdr",keep_significant_only = F,cluster_rows = F)+
  ggtitle("coinhibitory Luminal"),title = "Luminal")

print_tab(plot_cpdb(cell_type1 = 'CD|B|FC', cell_type2 = 'Myo', scdata = acc_cancer_cd45_caf,
          idents = 'cell_type', means = means, pvals = pvals,
          gene.family = 'coinhibitory',return_table = F,max_size = 4,p.adjust.method = "fdr",keep_significant_only = F,cluster_rows = F)+
  ggtitle("coinhibitory Myo"),title = "Myo")

print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|FC',cell_type2_a  = 'Luminal',cell_type2_b = "Myo",gene.family = "coinhibitory")
,title = "unique in luminal")


print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|FC',cell_type2_a  = 'Myo',cell_type2_b = "Luminal",gene.family = "coinhibitory")
,title = "unique in myo")

print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|FC',cell_type2_a  = 'CAF',cell_type2_b = "Myo|Luminal",gene.family = "coinhibitory")
,title = "unique in CAF")

```

# Chemokines interactions {.tabset}
```{r fig.height=6, results='asis'}
print_tab(
  plot_cpdb(cell_type1 = 'CD|B|FC', cell_type2 = 'Luminal', scdata = acc_cancer_cd45_caf,
          idents = 'cell_type', means = means, pvals = pvals,
          gene.family = 'chemokines',return_table = F,max_size = 4,p.adjust.method = "fdr",keep_significant_only = F,cluster_rows = F)+
  ggtitle("chemokines Luminal"),title = "Luminal")

print_tab(
  plot_cpdb(cell_type1 = 'CD|B|FC', cell_type2 = 'Myo', scdata = acc_cancer_cd45_caf,
          idents = 'cell_type', means = means, pvals = pvals,
          gene.family = 'chemokines',return_table = F,max_size = 4,p.adjust.method = "fdr",keep_significant_only = F,cluster_rows = F)+
  ggtitle("chemokines Myo"),title = "Myo")


print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|FC',cell_type2_a  = 'Luminal',cell_type2_b = "Myo",gene.family = "chemokines")
,title = "unique in luminal")


print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|FC',cell_type2_a  = 'Myo',cell_type2_b = "Luminal",gene.family = "chemokines")
,title = "unique in myo")

print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|FC',cell_type2_a  = 'CAF',cell_type2_b = "Myo|Luminal",gene.family = "chemokines")
,title = "unique in CAF")
```
# Chemokine ligands {.tabset}
```{r results='asis'}
genes = c("CXCL1\\D", "CXCL2\\D","CXCL3\\D","CXCL17","C3","CXCL14")
print_tab(plot_cpdb(cell_type1 = 'CD|B|FC', cell_type2 = 'Myo', scdata = acc_cancer_cd45_caf,
    idents = 'cell_type', means = means, pvals = pvals,
 genes = genes,return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F) 
 ,title = "Myo")

print_tab(plot_cpdb(cell_type1 = 'CD|B|FC', cell_type2 = 'Luminal', scdata = acc_cancer_cd45_caf,
    idents = 'cell_type', means = means, pvals = pvals,
  genes = genes,return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F) 
,title = "Luminal")


print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|FC',cell_type2_a  = 'Luminal',cell_type2_b = "Myo", genes = genes)
,title = "unique in luminal")


print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|FC',cell_type2_a  = 'Myo',cell_type2_b = "Luminal", genes = genes)
,title = "unique in myo")

print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|FC',cell_type2_a  = 'CAF',cell_type2_b = "Myo|Luminal", genes = genes)
,title = "unique in CAF")
```
# CCL22 and CCL28 {.tabset}
```{r results='asis'}
print_tab(plot_cpdb(cell_type1 = 'CD|B|FC', cell_type2 = 'Myo', scdata = acc_cancer_cd45_caf,
    idents = 'cell_type', means = means, pvals = pvals,
 genes = c("CCL22", "CCL28" ),return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F),title = "Myo")

print_tab(plot_cpdb(cell_type1 = 'CD|B|FC', cell_type2 = 'Luminal', scdata = acc_cancer_cd45_caf,
    idents = 'cell_type', means = means, pvals = pvals,
  genes = c("CCL22", "CCL28" ),return_table = F,max_size = 6,p.adjust.method = "fdr" ,keep_significant_only = F),title = "Luminal")



```

```{r fig.height=6}
plot_cpdb(cell_type1 = 'CD|B|FC', cell_type2 = 'Myo', scdata = acc_cancer_cd45_caf,
    idents = 'cell_type', means = means, pvals = pvals,
 genes = c("JAG", "MYB" ),return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F) 

plot_cpdb(cell_type1 = 'CD|B|FC', cell_type2 = 'Luminal', scdata = acc_cancer_cd45_caf,
    idents = 'cell_type', means = means, pvals = pvals,
  genes = c("JAG", "MYB" , "NOTCH","HES1","HEY"),return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F) 


```

<script src="https://hypothes.is/embed.js" async></script>

