---
title: '`r rstudioapi::getSourceEditorContext()$path %>% basename() %>% gsub(pattern = "\\.Rmd",replacement = "")`' 
author: "Avishai Wizel"
date: '`r Sys.time()`'
output: 
  html_notebook: 
    code_folding: hide
    toc: yes
    toc_collapse: yes
    toc_float: 
      collapsed: FALSE
    number_sections: true
    toc_depth: 1
---



# Functions

```{r warning=FALSE}
```

# Data

```{r}
acc_immune = LoadH5Seurat(file = "./Data/acc_immune_5KvarGenes_V2_cellIdentity.h5seurat")
```


```{r}
acc_immune$origin  %<>%  gsub(pattern = "Primary",replacement = "pri")
ident_origin = FetchData(object = acc_immune,vars = c("origin","cell_identity"))
ident_origin$combine = paste(ident_origin$cell_identity , ident_origin$origin)
ident_origin$general_identity = ident_origin$cell_identity
acc_immune %<>% AddMetaData(metadata = ident_origin[,"combine", drop=F],col.name = "cell_identity")
DimPlot(acc_immune,group.by  = "cell_identity")
```
# Antigen presenting machinery {.tabset}
```{r}
apm_genes = c("HLA-A","HLA-B","HLA-C","B2M","TAP1","TAP2", "TAPBP")
apm_score = FetchData(acc_immune,vars = apm_genes,slot = "data") %>% rowMeans()
acc_immune = AddMetaData(object = acc_immune,metadata = apm_score,col.name = "APM_score")
```

```{r fig.height=10, fig.width=10, results='asis'}
print_tab(plt = FeaturePlot(acc_immune,features = apm_genes),title = "genes")
print_tab(plt = VlnPlot(object = acc_immune,features = apm_genes,group.by = "cell_identity")
,title = "genes violin")

print_tab(plt = FeaturePlot(acc_immune,features = "APM_score"),title = "score")
```

# Exhaustion markers {.tabset}
```{r fig.height=8, fig.width=10,results='asis'}
exhausted_genes = c("PDCD1","CD244","CD160","CTLA4","HAVCR2")
print_tab(plt = FeaturePlot(acc_immune,features = exhausted_genes),title = "UMAP")
print_tab(plt = VlnPlot(object = acc_immune,features = exhausted_genes,group.by = "cell_identity"),title = "Violin plot")

```
# Immune receptors {.tabset}
```{r fig.height=8, fig.width=10, results='asis'}
receptors = c("CCR3", "CCR4", "CCR10","CXCR2", "CXCR3", "CXCR4", "IL17A")
print_tab(plt = FeaturePlot(acc_immune,features = receptors), title = "UMAP")
print_tab(plt = VlnPlot(object = acc_immune,features = receptors,group.by = "cell_identity"),title = "Violin plot")

```

# CellphoneDB {.tabset}
```{r}
acc_cancer_cells = readRDS("/sci/labs/yotamd/lab_share/avishai.wizel/R_projects/ACC_microenv/Data/acc_tpm_nCount_mito_no146_15k_cancercells.rds")
acc_caf = readRDS("/sci/labs/yotamd/lab_share/ACC/ACC_sc/analysis/acc_tpm_nCount_mito_no146_cafs.rds")
```

```{r}
# merge cancer, immune and CAF
common_genes = rownames(acc_cancer_cells) %>% intersect (rownames(acc_immune)) %>% intersect(rownames(acc_caf_cells))
acc_cancer_and_cd45 = merge(acc_cancer_cells[common_genes,],acc_immune[common_genes,])
overlapping_cells = colnames(acc_cancer_cells) %>% intersect(colnames(acc_caf)) 
acc_cancer_cd45_caf = merge(acc_cancer_and_cd45[common_genes,],acc_caf_cells[common_genes,!colnames(acc_caf_cells) %in% overlapping_cells] )
```

```{r}
#create origin metadata in acc
ln_plates = c("ACC22.LN.P11", "ACC22.P12.LN",  "ACC7.P13" )
acc_origin = FetchData(object = acc_cancer_cells,vars = "orig.ident") %>% mutate(origin = if_else(condition = orig.ident %in% ln_plates,true = "LN",false = "pri"))
acc_cancer_cells %<>% AddMetaData(metadata = acc_origin[,"origin",drop=F],col.name = "origin")
```

```{r}
#create origin metadata in caf
ln_plates = c("ACC22.LN.P11", "ACC22.P12.LN",  "ACC7.P13" )
caf_origin = FetchData(object = acc_caf,vars = "orig.ident") %>% mutate(origin = if_else(condition = orig.ident %in% ln_plates,true = "LN",false = "pri"))
acc_caf %<>% AddMetaData(metadata = caf_origin[,"origin",drop=F],col.name = "origin")
```

```{r}
  #create metadata

#create luminal_over_myo
gs=acc_cancer_cells@assays$RNA@var.features
myoscore=apply(acc_cancer_cells@assays$RNA@scale.data[intersect(c("TP63","TP73","CAV1","CDH3","KRT5","KRT14","ACTA2","TAGLN","MYLK","DKK3"),gs),],2,mean)
lescore=apply(acc_cancer_cells@assays$RNA@scale.data[intersect(c("KIT","EHF","ELF5","KRT7","CLDN3","CLDN4","CD24","LGALS3","LCN2","SLPI"),gs),],2,mean)
acc_cancer_cells=AddMetaData(acc_cancer_cells,lescore-myoscore,"luminal_over_myo")

#create lum_or_myo
lum_over_myo = FetchData(object = acc_cancer_cells,vars = "luminal_over_myo")
lum_over_myo$lum_or_myo = "Unknown"
lum_over_myo$lum_or_myo [lum_over_myo$luminal_over_myo>1]  = "Luminal"
lum_over_myo$lum_or_myo [lum_over_myo$luminal_over_myo<(-1)]  = "Myo"
lum_or_myo = lum_over_myo[,"lum_or_myo",drop = F]

lum_or_myo$combine = paste(lum_or_myo$lum_or_myo , acc_cancer_cells$origin) #add environment
acc_cancer_cells %<>% AddMetaData(metadata = lum_or_myo[,"combine",drop=F],col.name = "cell_identity")

#add envirinment to CAF identity
acc_caf$cell_identity = paste(acc_caf$cell.type , acc_caf$origin) #add environment

```

```{r}
#create  metadata

# combine
immune_identity =FetchData(object = acc_immune,vars = "cell_identity")
caf_identity =FetchData(object = acc_caf,vars = "cell_identity")
cancer_identity =FetchData(object = acc_cancer_cells,vars = "cell_identity")%>% filter(!cell_identity %in% c("Unknown pri","Unknown LN")) #remove unknown cells

all_identity = do.call("rbind", list(cancer_identity, immune_identity, caf_identity))

#rename and sort columns
all_identity$barcode_sample = rownames(all_identity)
all_identity = all_identity %>% rename(cell_type = cell_identity)
all_identity = all_identity[,c(2,1)]
```

```{r}
#create  enviroment
immune_enviroment = FetchData(object = acc_immune,vars = c("cell_identity", "origin")) %>% set_names(c("cell_type","microenviroment"))
acc_enviroment = FetchData(object = acc_cancer_cells,vars = c("cell_identity", "origin"))%>%
  filter(!cell_identity %in% c("Unknown pri","Unknown LN"))%>%  #remove unknown 
  set_names(c("cell_type","microenviroment"))
caf_enviroment = FetchData(object = acc_caf,vars = c("cell_identity", "origin")) %>% set_names(c("cell_type","microenviroment"))

all_environment = do.call("rbind", list(immune_enviroment, acc_enviroment, caf_enviroment))
all_environment = data.frame(cell_type = all_environment$cell_type %>% unique()) %>% mutate(microenviroment = if_else(condition = grepl(x =  cell_type,pattern =  "LN"),true = "LN",false = "pri")) # fix environment contain every cell type, not every cell

```


```{r}
write.table(x = all_identity,file = "./Data/CellphoneDB/input_V2/metadata.tsv",row.names =F,sep = "\t")
write.table(x = all_environment,file = "./Data/CellphoneDB/input_V2/enviroment.tsv",row.names =F,sep = "\t")
```

```{r}
acc_cancer_cd45_caf = acc_cancer_cd45_caf[,rownames(all_identity)]
fwrite(as.data.frame(acc_cancer_cd45_caf@assays[["RNA"]]@data), file = "./Data/CellphoneDB/input_V2/counts.txt",sep = "\t",row.names = T)
```


```{python include=FALSE}
#download database
import pandas as pd
import glob
import os
# -- Version of the databse
cpdb_version = 'v4.1.0'

# -- Path where the input files to generate the database are located
cpdb_target_dir = os.path.join('./Data/CellphoneDB/', cpdb_version)

# Download database
from cellphonedb.utils import db_utils
db_utils.download_database(cpdb_target_dir, cpdb_version)
```

```{python include=FALSE}
from cellphonedb.src.core.methods import cpdb_statistical_analysis_method
folder = "input_V2"
folder_output = "output_V2"
deconvoluted, means, pvalues, significant_means = cpdb_statistical_analysis_method.call(
    cpdb_file_path = "./Data/CellphoneDB/v4.1.0/cellphonedb.zip",                 # mandatory: CellPhoneDB database zip file.
    meta_file_path = "./Data/CellphoneDB/"+folder+"/metadata.tsv",                 # mandatory: tsv file defining barcodes to cell label.
    counts_file_path = "./Data/CellphoneDB/"+folder+"/counts.txt",             # mandatory: normalized count matrix.
    counts_data = 'hgnc_symbol',                     # defines the gene annotation in counts matrix.
     microenvs_file_path = "./Data/CellphoneDB/"+folder+"/enviroment.tsv",
    output_path = "./Data/CellphoneDB/" + folder_output, # Path to save results.
    output_suffix = "" 
)
```   


```{r}
library(ktplots)
library(reticulate)
acc_cancer_cd45_caf$cell_type = all_identity[,2,drop = F] # add cells identities to Seurat

#read data:
# pvals =  py$pvalues
# means = py$means

# #or:
pvals = read.delim("./Data/CellphoneDB/output_V2/statistical_analysis_pvalues_.txt",check.names = F)
means = read.delim("./Data/CellphoneDB/output_V2/statistical_analysis_means_.txt",check.names = F)

```


```{r}
trace(plot_cpdb_heatmap,edit = T)
untrace(plot_cpdb_heatmap)
undebug(plot_cpdb_heatmap)
mat = plot_cpdb_heatmap(scdata = acc_cancer_cd45_caf, idents = 'cell_type',pvals =  pvals,main = "Number of significant interactions",alpha = 0.05,treeheight_row = 50,return_tables = T)
```


```{r}
rownames(all_environment) = all_environment$cell_type
all_environment$cell_type <- NULL
```

```{r echo=TRUE, fig.height=8, fig.width=18, results='asis'}
ln_types = all_environment %>% filter(microenviroment == "LN") %>% rownames()
pri_types = all_environment %>% filter(microenviroment == "pri") %>% rownames()


p1= pheatmap::pheatmap(mat$count_network[pri_types,pri_types],main = "Number of significant interactions- primary",silent = T) [[4]]
p2 = pheatmap::pheatmap(mat$count_network[ln_types,ln_types],main = "Number of significant interactions- LN",silent = T)[[4]]
gridExtra::grid.arrange(p1, p2,nrow = 1,ncol=2)
```

```{r}
uniq_interactions <- function(cell_type1, cell_type2_a ,cell_type2_b, gene.family = NULL,genes = NULL) {
  require(purrr)
  a = plot_cpdb(cell_type1 = cell_type1, cell_type2 =cell_type2_a, scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = gene.family,return_table = T, p.adjust.method = "fdr",keep_significant_only = F, genes = genes)
  
  b = plot_cpdb(cell_type1 = cell_type1, cell_type2 = cell_type2_b, scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = gene.family,return_table = T,p.adjust.method = "fdr",keep_significant_only = F, genes = genes)
  
  
  all = list()
  i=0
  nelements = a$Var2 %>% unique() %>% length()
  a_couples = a$Var2 %>% unique()%>% as.vector()  
  b_couples = b$Var2 %>% unique()%>% as.vector()  
  for (i in 1:nelements) {
    sig_couples_a = a %>% filter(Var2 == a_couples[i]) %>% filter(pvals_adj <= 0.05) %>%  pull(Var1) %>% as.vector()  
    sig_couples_b = b %>% filter(Var2 == b_couples[i]) %>% filter(pvals_adj <= 0.05) %>%  pull(Var1) %>% as.vector()  
    only_in_a = sig_couples_a[! sig_couples_a %in% sig_couples_b]
    all[[a_couples[i]]] = only_in_a 
    i = i+1
  }
  all = t(map_dfr(all, ~as_tibble(t(.)))) %>% as.data.frame() %>%  set_names(a_couples)
  return(all)
}


trace(plot_cpdb,edit = T)
```

```{r}
# switch_interactions <- function(x,pattern) {
#   index = lapply(x, grepRaw,pattern = pattern) %>% as_vector()
#   first_gene = substr(x = x, start = 1, stop = index-1)
#   second_gene = substr(x = x, start = index+length(pattern), stop = nchar(x))
#   inverted = paste0(second_gene,"-",first_gene)
# }

switch_genes <- function(row) {
  first_gene = row[14]
  if (is_null(first_gene)) {first_gene = row[16] %>% gsub(pattern = "complex:",replacement = "")}
  second_gene = row[15]
  if (is_null(second_gene)) {first_gene = row[17] %>% gsub(pattern = "complex:",replacement = "")}

  inverted = paste0(second_gene,"-",first_gene)
}
```

```{r}
my_plot_cpdb <- function(...,caf = F) {
  p = plot_cpdb(...)
  pg <- ggplot_build(p)
  p_pairs = pg$plot$data$Var1 %>% gsub(pattern = "-",replacement = "_")
  pval_cut = pvals %>%  column_to_rownames(var = "interacting_pair")  
  pval_cut = pval_cut[p_pairs,c("receptor_a","receptor_b","gene_a","gene_b","partner_a","partner_b")]
  
  pg$plot$data = cbind(pg$plot$data, pval_cut)
  rows_to_switch = pg$plot$data$receptor_a == "False" & pg$plot$data$receptor_b == "True"
  debug(switch_genes)
  a = apply(pg$plot$data[169:179,], MARGIN = 1, switch_genes) 

  if (caf == F){
    pg$plot$data  %<>%  mutate(lum_or_myo = if_else(condition = grepl(pattern = "Luminal",x = Var2),true = "Luminal",false = "Myo")) %>% mutate(
      direction =if_else(condition = grepl(pattern = "-Luminal|-Myo",x = Var2),true = "cancel-immune",false = "immune-cancer")) 
      pg$plot+facet_grid(cols = vars(direction,lum_or_myo),scales = "free_x")+ylab("Interacting pair") +
      theme(axis.title.y = element_text(angle = 90,size = 20))
      
  }else{
    pg$plot$data  %<>%  mutate(direction =if_else(condition = grepl(pattern = "-CAF",x = Var2),true = "CAF-immune",false = "immune-CAF")) 
      pg$plot+facet_grid(cols = vars(direction),scales = "free_x")+ylab("Interacting pair") +
      theme(axis.title.y = element_text(angle = 90,size = 20))
  }
  

}
```


# Costimulatory interactions {.tabset}
```{r fig.height=12, fig.width=20, results='asis'}

print_tab(plt = 
            my_plot_cpdb(cell_type1 = 'CD|B|Macro|mono', cell_type2 = 'Luminal pri|Myo pri', scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = 'costimulatory',return_table = F,max_size = 3,p.adjust.method = "fdr",keep_significant_only = T,cluster_rows = T)+
            ggtitle("Costimulatory primary")
  ,title = "Primary")


print_tab(plt = 
            my_plot_cpdb(cell_type1 = 'CD|B|Macro|mono', cell_type2 = 'Luminal LN|Myo LN', scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = 'costimulatory',return_table = F,max_size = 3,p.adjust.method = "fdr",keep_significant_only = T,cluster_rows = F)+
            ggtitle("Costimulatory LN")
  ,title = "LN")

print_tab(plt = 
            my_plot_cpdb(cell_type1 = 'CD|B|Macro|mono', cell_type2 = 'CAF', scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = 'costimulatory',return_table = F,max_size = 3,p.adjust.method = "fdr",keep_significant_only = T,cluster_rows = F,caf = T)+
            ggtitle("Costimulatory CAF")
  ,title = "CAF")

print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|Macro|mono',cell_type2_a  = 'Luminal pri',cell_type2_b = "Myo",gene.family = "Costimulatory")
,title = "unique in luminal pri")


print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|Macro|mono',cell_type2_a  = 'Myo pri',cell_type2_b = "Luminal",gene.family = "Costimulatory")
,title = "unique in myo pri")

print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|Macro|mono',cell_type2_a  = 'Luminal LN',cell_type2_b = "Myo",gene.family = "Costimulatory")
,title = "unique in luminal LN")


print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|Macro|mono',cell_type2_a  = 'Myo LN',cell_type2_b = "Luminal",gene.family = "Costimulatory")
,title = "unique in myo LN")

```



# Coinhibitory interactions {.tabset}

```{r fig.height=5,results='asis'}
print_tab(my_plot_cpdb(cell_type1 = 'CD|B|Macro|mono', cell_type2 = 'Luminal pri|Myo pri', scdata = acc_cancer_cd45_caf,
          idents = 'cell_type', means = means, pvals = pvals,
          gene.family = 'coinhibitory',return_table = F,max_size = 4,p.adjust.method = "fdr",keep_significant_only = F,cluster_rows = F)+
  ggtitle("coinhibitory primary"),title = "Primary")

print_tab(my_plot_cpdb(cell_type1 = 'CD|B|Macro|mono', cell_type2 = 'Luminal LN|Myo LN', scdata = acc_cancer_cd45_caf,
          idents = 'cell_type', means = means, pvals = pvals,
          gene.family = 'coinhibitory',return_table = F,max_size = 4,p.adjust.method = "fdr",keep_significant_only = F,cluster_rows = F)+
  ggtitle("coinhibitory LN"),title = "LN")


print_tab(plt = 
            my_plot_cpdb(cell_type1 = 'CD|B|Macro|mono', cell_type2 = 'CAF', scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = 'coinhibitory',return_table = F,max_size = 3,p.adjust.method = "fdr",keep_significant_only = T,cluster_rows = F,caf = T)+
            ggtitle("coinhibitory CAF")
  ,title = "CAF")

print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|Macro|mono',cell_type2_a  = 'Luminal LN',cell_type2_b = "Myo LN",gene.family = "coinhibitory")
,title = "unique in luminal LN")


print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|Macro|mono',cell_type2_a  = 'Myo LN',cell_type2_b = "Luminal LN",gene.family = "coinhibitory")
,title = "unique in myo LN")


print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|Macro|mono',cell_type2_a  = 'Luminal pri',cell_type2_b = "Myo pri",gene.family = "coinhibitory")
,title = "unique in luminal pri")

print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|Macro|mono',cell_type2_a  = 'Myo pri',cell_type2_b = "Luminal pri",gene.family = "coinhibitory")
,title = "unique in myo pri")
```

# Chemokines interactions {.tabset}
```{r fig.height=7, results='asis'}
print_tab(
  my_plot_cpdb(cell_type1 = 'CD|B|Macro|mono', cell_type2 = 'Luminal pri|Myo pri', scdata = acc_cancer_cd45_caf,
          idents = 'cell_type', means = means, pvals = pvals,
          gene.family = 'chemokines',return_table = F,max_size = 4,p.adjust.method = "fdr",keep_significant_only = F,cluster_rows = F)+
  ggtitle("chemokines primary"),title = "Primary")

print_tab(
  my_plot_cpdb(cell_type1 = 'CD|B|Macro|mono', cell_type2 = 'Luminal LN|Myo LN', scdata = acc_cancer_cd45_caf,
          idents = 'cell_type', means = means, pvals = pvals,
          gene.family = 'chemokines',return_table = F,max_size = 4,p.adjust.method = "fdr",keep_significant_only = F,cluster_rows = F)+
  ggtitle("chemokines LN"),title = "LN")



print_tab(plt = 
            my_plot_cpdb(cell_type1 = 'CD|B|Macro|mono', cell_type2 = 'CAF', scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      gene.family = 'chemokines',return_table = F,max_size = 3,p.adjust.method = "fdr",keep_significant_only = T,cluster_rows = F,caf = T)+
            ggtitle("chemokines CAF")
  ,title = "CAF")

print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|Macro|mono',cell_type2_a  = 'Luminal LN',cell_type2_b = "Myo LN",gene.family = "chemokines")
,title = "unique in luminal LN")


print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|Macro|mono',cell_type2_a  = 'Myo LN',cell_type2_b = "Luminal LN",gene.family = "chemokines")
,title = "unique in myo LN")


print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|Macro|mono',cell_type2_a  = 'Luminal pri',cell_type2_b = "Myo pri",gene.family = "chemokines")
,title = "unique in luminal pri")

print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|Macro|mono',cell_type2_a  = 'Myo pri',cell_type2_b = "Luminal pri",gene.family = "chemokines")
,title = "unique in myo pri")
```
# Chemokine ligands {.tabset}
```{r fig.height=8, results='asis'}
genes = c("CXCL1\\D", "CXCL2\\D","CXCL3\\D","CXCL17","C3","CXCL14")
print_tab(my_plot_cpdb(cell_type1 = 'CD|B|Macro|mono', cell_type2 = 'Luminal pri|Myo pri', scdata = acc_cancer_cd45_caf,
    idents = 'cell_type', means = means, pvals = pvals,
 genes = genes,return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F) 
 ,title = "Primary")

print_tab(my_plot_cpdb(cell_type1 = 'CD|B|Macro|mono', cell_type2 = 'Luminal LN|Myo LN', scdata = acc_cancer_cd45_caf,
    idents = 'cell_type', means = means, pvals = pvals,
  genes = genes,return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F) 
,title = "LN")


print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|Macro|mono',cell_type2_a  = 'Luminal LN',cell_type2_b = "Myo LN",genes = genes)
,title = "unique in luminal LN")


print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|Macro|mono',cell_type2_a  = 'Myo LN',cell_type2_b = "Luminal LN",genes = genes)
,title = "unique in myo LN")


print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|Macro|mono',cell_type2_a  = 'Luminal pri',cell_type2_b = "Myo pri",genes = genes)
,title = "unique in luminal pri")

print_tab(plt = 
            uniq_interactions(cell_type1 = 'CD|B|Macro|mono',cell_type2_a  = 'Myo pri',cell_type2_b = "Luminal pri",genes = genes)
,title = "unique in myo pri")
```
# CCL22 and CCL28 {.tabset}
```{r results='asis'}
print_tab(my_plot_cpdb(cell_type1 = 'CD|B|Macro|mono', cell_type2 = 'Luminal pri|Myo pri', scdata = acc_cancer_cd45_caf,
    idents = 'cell_type', means = means, pvals = pvals,
 genes = c("CCL22", "CCL28" ),return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F),title = "Primary")

print_tab(my_plot_cpdb(cell_type1 = 'CD|B|Macro|mono', cell_type2 = 'Luminal LN|Myo LN', scdata = acc_cancer_cd45_caf,
    idents = 'cell_type', means = means, pvals = pvals,
  genes = c("CCL22", "CCL28" ),return_table = F,max_size = 6,p.adjust.method = "fdr" ,keep_significant_only = F),title = "LN")



```

# Notch signaling interactions with immune {.tabset}
```{r fig.height=6, results='asis'}
print_tab(plt = 
            my_plot_cpdb(cell_type1 = 'CD|B|Macro|mono', cell_type2 = 'Luminal pri|Myo pri', scdata = acc_cancer_cd45_caf,
                         idents = 'cell_type', means = means, pvals = pvals,
                         genes =c("JAG", "MYB" , "NOTCH","HES1","HEY"),return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F) 
        ,title = "Primary")

print_tab(plt = 
            my_plot_cpdb(cell_type1 = 'CD|B|Macro|mono', cell_type2 = 'Luminal LN|Myo LN', scdata = acc_cancer_cd45_caf,
                         idents = 'cell_type', means = means, pvals = pvals,
                         genes =c("JAG", "MYB" , "NOTCH","HES1","HEY"),return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F) 
        ,title = "Primary")
```

# Notch signaling interactions with CAF {.tabset}

```{r fig.height=6 ,results='asis'}
print_tab(plt = 
            plot_cpdb(cell_type1 = 'CAF', cell_type2 = 'Luminal pri|Myo pri', scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      genes = c("JAG", "MYB" ),return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F) 
          ,title = "Primary")

print_tab(plt = 
            plot_cpdb(cell_type1 = 'CAF', cell_type2 = 'Luminal LN|Myo LN', scdata = acc_cancer_cd45_caf,
                      idents = 'cell_type', means = means, pvals = pvals,
                      genes = c("JAG", "MYB" ),return_table = F,max_size = 4,p.adjust.method = "fdr" ,keep_significant_only = F) 
          ,title = "Primary") 
```

<script src="https://hypothes.is/embed.js" async></script>

